Proposed Solution

### 2017-01-25 CAV17/secs/postanal.tex
cav17: sec 6

\section{Post Analysis}

\app can output the set of learned rules from the training set as
described in $\S$\ref{sec-learn}. Recall that a rule is 
an implication relationship of the form $r = X \implies p(X,Y)$.
This data is sufficient for \app to perform its core task of
configuration file validation, but can be used for more than 
simple rule checking. By interpreting the rules as a graph (which
we call the {\bf Rule Graph}), we can 
use tools from graph theory to extract information
about the configuration space. We inspect properties of this 
Rule Graph to sort reported errors by those most likely to be valid.
To demonstrate the additional value of the Rule Graph, we
also use it to estimate the complexity of configuration settings.

Accessibility of the Rule Graph is a useful property of the association 
rule learning technique applied by \app.
In contrast, the model output from a neural network is not as easily 
amenable to analysis \cite{nnAnalysis1, nnAnalysis2}, making it harder
to build on the work of previously developed methods and tools.
The following section provides a precise definition of the Rule Graph
and the metrics derived for the purposes of ranking reported errors
and complexity analysis.

@@

We define the \textit{Rule Graph} as a directed hypergraph $H = (V,E)$,
   with vertices $V = \{ keywords \}$ and labeled, weighted edges $E = \{ (V_s, V_t, l, w) \}$.
The set of edges is constructed from the learned rules, using the source and target keyword sets as sources and targets respectively, the predicates as labels, and the confidence as weights:
%
\begin{align*}
\forall r \in & Learn(\trainingSet).\ \exists e\ \in E.\\
              & V_s = X_r \land V_t=Y_r \land l=p_r \land w = confidence(r)
\end{align*}

@@

    $$RANK(r) = \frac{\sum_{k \in K} \mathcal{D}(k)}{|K|}$$

>>>>

\section{Rule Graph Analysis}
\label{sec-post}

\app can output the set of learned rules from the training set (as
described in Sec.~\ref{sec-learn}). Recall that a rule is 
an implication relationship of the form $r = X \implies p(X,Y)$.
This data is sufficient for \app to perform its core task of
configuration file verification, but can be used for more than 
simple rule checking. By interpreting the rules as a graph (which
we call the {\bf Rule Graph}), we can 
use tools from graph theory to extract information
about the configuration space. We inspect properties of this 
Rule Graph to sort reported errors by those most likely to be valid.
To demonstrate the additional value of the Rule Graph, we
also use it to estimate the complexity of configuration settings.

Accessibility of the Rule Graph is a useful property of the association 
rule learning technique applied by \app.
In contrast, the model output from a neural network is not as easily 
amenable to analysis~\cite{nnAnalysis1, nnAnalysis2}, making it harder
to build on the work of previously developed methods and tools.
The following section provides a precise definition of the Rule Graph
and the metrics derived for the purposes of ranking reported errors
and complexity analysis.

@@

We define the \textit{Rule Graph} as a directed hypergraph $H = (V,E)$,
   with vertices $V = \{ keywords \}$ and labeled, weighted edges $E = \{ (V_s, V_t, l, w) \}$.
The set of edges is constructed from the learned rules, using the source and target keyword sets as sources and targets respectively, the predicates as labels, and the confidence as weights:
%
\begin{align*}
\forall r \in & Learn(\trainingSet).\ \exists e\ \in E.\\
              & V_s = X_r \land V_t=Y_r \land l=p_r \land w =
\textit{confidence(r)}
\end{align*}

@@

    $$\textit{RANK(r)} = \frac{\sum_{k \in K} \mathcal{D}(k)}{|K|}$$
